Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-13 paper.tex
wordings in section 1

\noindent \textcolor{red}{TODO: Focus on the experience we accumulated (general remark)}\\
\textcolor{red}{TODO: Motivate our design choices.}

@@

The \sklearn project \citep{pedregosa2011} is an open source
machine learning library for the Python programming language. The ambition of
the project is to provide efficient and well-established machine learning tools
within a programming environment that is accessible to non-machine learning
experts and reusable in various scientific areas. In itself the project isn't
a novel domain-specific language, but a library that provides machine
learning idioms to a general-purpose high-level language. Among other things,
it includes classical learning algorithms, model selection tools and
preprocessing procedures.

The project is a programming library, i.e. a collection of classes -- in the
object-oriented sense -- that users import into Python programs. Using \sklearn
therefore requires basic Python programming knowledge. No command-line
interface, let alone a graphical user interface, is offered for non-programmer
users. Instead, interactive use is made possible by the Python interactive
interpreter, and its enhanced replacement IPython \citep{perez2007ipython},
which offer a \textsc{matlab}-like working environment specifically designed for
scientific use.

From its core, the library has been designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries. NumPy
\citep{vanderwalt2011} augments Python with a numeric array datatype and
associated array computing primitives while SciPy \citep{varoquaux2013scipy}
extends it further by making common numeric operations available, either by
implementing those in Python/NumPy or by wrapping existing
C/C{}\verb!++!/Fortran implementations. In a similar vein, \sklearn extends
Python with a set of composable machine learning operations.

@@

In a previous paper \citep{pedregosa2011}, \sklearn was briefly presented and
benchmarked against several competitors. In this paper, we instead focus on an
in-depth discussion and analysis of the design choices used in building the
library. First, in section \ref{sec:core-api}, we present the central application
programming interface (API) and then describe, in section \ref{sec:advanced-api},
advanced API mechanisms built from the core interface. Section
\ref{sec:implementation} describes implementation trade-offs and analyzes
limitations of the technologies we rely on, while section
\ref{sec:comparison} then compares \emph{scikit-learn} to other major projects in
terms of API. Finally, conclusions and directions of future works are included
in section \ref{sec:conclusions}.

>>>>

@@

The \sklearn project \citep{pedregosa2011} is an open source machine learning
library for the Python programming language. The ambition of the project is to
provide efficient and well-established machine learning tools within a
programming environment that is accessible to non-machine learning experts and
reusable in various scientific areas. The project is not a novel domain-specific
language, but a library that provides machine learning idioms to a general-
purpose high-level language. Among other things, it includes classical learning
algorithms, model selection tools and preprocessing procedures.

In itself, the project is a programming library, i.e. a collection of classes
and functions that users import into Python programs. Using \sklearn therefore
requires basic Python programming knowledge. No command-line interface, let
alone a graphical user interface, is offered for non-programmer users. Instead,
interactive use is made possible by the Python interactive interpreter, and its
enhanced replacement IPython \citep{perez2007ipython}, which offer a
\textsc{matlab}-like working environment specifically designed for scientific
use.

From its core, the library has been designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries. NumPy
\citep{vanderwalt2011} augments Python with a numeric array datatype and proper
array computing primitives while SciPy \citep{varoquaux2013scipy} extends it
further by making common numerical operations available, either by implementing
those in Python/NumPy or by wrapping existing C/C{}\verb!++!/Fortran
implementations. In a similar vein, \sklearn extends Python with a set of
composable machine learning operations.

@@

In a previous paper \citep{pedregosa2011}, \sklearn was briefly presented and
benchmarked against several competitors. In this paper, we instead focus on an
in-depth discussion and analysis of the design choices used in building the
library. We first present in section \ref{sec:core-api} the central application
programming interface (API) and then describe, in section \ref{sec:advanced-api},
advanced API mechanisms built from the core interface. Section
\ref{sec:implementation} describes implementation trade-offs and discusses
limitations of the technologies we rely on. Section \ref{sec:comparison}
then compares \emph{scikit-learn} to other major projects in terms of API.
Finally, conclusions and directions of future works are included in section
\ref{sec:conclusions}.
